PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added PCL difference score for prepan and baseline

>>>>

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
# Difference score for prepandemic and baseline pcl sum scores
dat.glad <- dat.glad %>%
  mutate(
    pcl.diff_score_prepan_base =
      as.numeric(
        pcl.sum_score_prepan - pcl.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

summary(dat.glad$pcl.diff_score_prepan_base)
```
